\huge A Better (One-Line!) Title Here

### 2016-10-20 pets2017-paper/pets2017-paper.tex
move citations deleted from recuitment section into the metholodgy section.
clarified that we prescreened due to small participant size in recuirments subsection.

Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
%http://www.usabilitybok.org/Formative-evaluation
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/

@@

Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process. A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
%http://www.usabilitybok.org/Summative-evaluation
%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
}

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics. We pre-screened~\cite{screening} to have diversity of gender, age, technical expertise, and self-reported familiarity with Tor. The complete pre-screening survey can be found in Appendix~\ref{qualitative-prescreening}.

>>>>

Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
%http://www.usabilitybok.org/Formative-evaluation
%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/ ~\cite{howmanyusers}

@@

Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process. A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience. This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
%http://www.usabilitybok.org/Summative-evaluation
%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
%~\cite{summative}
}

@@

\subsection{Recruitment}
We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics. We pre-screened~\cite{screening} to ensure diversity of gender, age, technical expertise, and (self-reported) familiarity with Tor in a small participant pool. The pre-screening survey is in Appendix~\ref{qualitative-prescreening}.
